---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 2


## 2.3

## First Question part a



```{r,warning=FALSE,message=FALSE,comment=NA}
a <- c(5, 12, 32, 50, 10000)
a
```

## First Question part b

```{r,warning=FALSE,message=FALSE,comment=NA}
b <- 1:100
b
```

\begin{center}
OR
\end{center}

```{r,warning=FALSE,message=FALSE,comment=NA}
b <- seq(1, 100)
b
```

\begin{center}
OR
\end{center}

```{r,warning=FALSE,message=FALSE,comment=NA}
b <- seq(1, 100, by=1)
b
```

\begin{center}
OR
\end{center}

```{r,warning=FALSE,message=FALSE,comment=NA}
b <- seq(1, 100, length.out = 100)
b
```
## First Question part c

```{r,warning=FALSE,message=FALSE,comment=NA}
c <- seq(2, 100, by=2)
c
```

## First Question part d

```{r,warning=FALSE,message=FALSE,comment=NA}
d <- rep(c(3, 6, 9), c(10, 20, 30))
d
```

## Second Question

```{r,warning=FALSE,message=FALSE,comment=NA}
e <- seq(1, 10, by=1)
e
```
\begin{center}
OR
\end{center}

```{r,warning=FALSE,message=FALSE,comment=NA}
e <- 1:10
e
```
\begin{center}
OR
\end{center}

```{r,warning=FALSE,message=FALSE,comment=NA}
e <- seq(1, 10, length.out = 10)
e
```






## Third Question

```{r,warning=FALSE,message=FALSE,comment=NA}
f <- rep(1:4, times=3)
f
```


## Fourth Question

```{r,warning=FALSE,message=FALSE,comment=NA}
n <- 1:100
sqrt_n <- sqrt(n)
sqrt_n
```

\begin{center}
OR
\end{center}


```{r,warning=FALSE,message=FALSE,comment=NA}

sqrt_n <- sqrt(1:100)
sqrt_n
```


\begin{center}
OR
\end{center}


```{r,warning=FALSE,message=FALSE,comment=NA}

sqrt_n <- sqrt(seq(1, 100))
sqrt_n
```


## Fifth Question

```{r,warning=FALSE,message=FALSE,comment=NA}
g <- seq(1, 100, by = 0.4)
g
```


# 2.6 Filtering vectors based on conditions


## 11)

```{r, warning=FALSE, comment= NA}

x <- c(80, 39, NA, 51, 51, 11, NA, NA, NA, 100, 80, 70)
```

### a).

```{r, warning=FALSE, comment= NA}


nonMissings <- x[!is.na(x)] # since is.na command gives us whether the value is a missing value or not 
nonMissings
```

### b).

```{r, comment=NA, echo=FALSE, eval=FALSE}
x[x %% 2 == 1]
```

```{r, warning=FALSE, comment= NA}


missingsOdd <- x[(x %% 2) != 0] # since missing values are already not even numbers
missingsOdd
```


### c).

```{r, comment=NA, echo=FALSE, eval=FALSE}
y <- x[x %% 2 == 1]
y[!is.na(y)]
```


```{r, warning=FALSE, comment= NA}

odd <- x[!is.na(x) & (x %% 2) != 0] # extracting only the values which are not odd
#ignoring missing values
odd
```

### d).

```{r, comment=NA, echo=FALSE, eval=FALSE}
x %in% 1:50
```

```{r, warning=FALSE, comment= NA}

x <- c(80, 39, NA, 51, 51, 11, NA, NA, NA, 100, 80, 70)
notIn <- x[!is.na(x) &!(x %in% 1:50)] # extracting only the values which not in the set 1:50
notIn
```
\newpage

# 2.7 Modify a vector

## 12)

```{r, warning=FALSE, comment= NA}

age <- c(20, 30, 40, 41, 32, 32, 25,  NA, NA, -4, -6, 9999, 10000)
```


### a).
```{r, warning=FALSE, comment= NA}

a <- replace(age, which(age < 0), NA) # assigning NA to negative values
a
```


### b).

```{r, warning=FALSE, comment= NA}

age <- c(20, 30, 40, 41, 32, 32, 25,  NA, NA, -4, -6, 9999, 10000)
age [age < 0] <- 0 # assigning zero for all negative values

valid <- age[age %in% 1:100] # extracting the valid responses

mean(valid, rm.na=TRUE)

```

## 13)

```{r, warning=FALSE, comment= NA}
set.seed(17620212)
b <- rnorm(100)
b
```

### a).


```{r, warning=FALSE, comment= NA}
b[1:5] <- 1 # changing the first five values to 1
b
```


### b).

```{r, warning=FALSE, comment= NA}
length(b) # length of the vector b
```
```{r, warning=FALSE, comment= NA}
b[96:100] <- 0 # changing last five values to 0
b
```

### c).

```{r, warning=FALSE, comment= NA}
b[b > 0.5] <- 1 # assigning 1 to values grater than 0.5
b
```

```{r, warning=FALSE, comment= NA}
b[b < 0.5] <- 0 # assigning 0 to values less than 0.5
b
```

### d).

```{r}
set.seed(17620212)
b <- rnorm(100)
b[b > 0.5] <- 1
b[b <= 0.5] <- 0
b
b[b == 0] <- "MALE"
b[b == 1] <- "FEMALE"
b
```


```{r, warning=FALSE, comment= NA}
b <- ifelse(b == 0, "MALE", "FEMALE")
b
```

Or else this can be done by using the following method as well.

```{r, warning=FALSE, comment= NA}
# b <- replace(b, which(b==0), "MALE")
# b <- replace(b, which(b==1), " FEMALE")

```









## 2.8

## i) Enter confirmed cases in table 1 to a vector.

```{r, warning=FALSE, message=FALSE, comment=NA}
confirmed_cases <- c(29631, 1151, 1104, 1073, 879, 830, 771, 492, 468, 459, 405, 337, 331, 
                     295, 261, 218, 213, 210, 141, 136, 119, 109, 107, 91, 85, 80, 58, 49, 
                     49, 36, 18, 18, 10, 1) # Initialize the vector

confirmed_cases # Print the vector

length(confirmed_cases) # To check the length of the vector

is.vector(confirmed_cases) # To check if it is a vector

is.integer(confirmed_cases) # To check if it is a vector of integers

class(confirmed_cases)

typeof(confirmed_cases)

# To check whether all confirmed cases are recorded by checking Total given in Table 1 
sum(confirmed_cases) 
```


## ii) Name the elements by province/regions/cities in China.

### Modifying the names of an existing vector

```{r, warning=FALSE, message=FALSE, comment=NA}
# Initialize the vector

names(confirmed_cases) <- c("Hubei", "Guangdong", "Zhejiang", "Henan", "Hunan", "Anhui", 
                            "Jiangxi", "Jiangsu", "Chongqing", "Shandong", "Sichuan", 
                            "Beijing", "Heilongjiang", "Shanghai", "Fujian", "Hebei", 
                            "Shaanxi", "Guangxi", "Yunnan", "Hainan", "Shanxi", 
                            "Guizhou", "Liaoning", "Tianjin", "Gansu", "Jilin", 
                            "Inner Mongolia", "Ningxia", "Xinjiang", "Hong Kong SAR", 
                            "Qinghai", "Taipei and environs", "Macao SAR", "Xizang") 


confirmed_cases # Print the vector
```


## iii) Write Rcodes to answer the following questions.

## a) Which province/region/city has the highest number of confirmed cases?

### Method 1:

```{r, warning=FALSE, message=FALSE, comment=NA}
# To get the province/ region/ city which has the highest value from the vector 
which.max(confirmed_cases) 
```


### Method 2:

```{r, warning=FALSE, message=FALSE, comment=NA}
max(confirmed_cases) # To get the the maximum value/ highest value from the vector

# If equal return as TRUE
# If not return as FALSE
# Check whether each value of the vector and return whether the value is equal to 
# the maximum value or not
confirmed_cases == max(confirmed_cases) 

# To select an element which equal to the condition
confirmed_cases[confirmed_cases == max(confirmed_cases)] 
```

## b) Number of confirmed cases reported in Hebei, China.

```{r, warning=FALSE, message=FALSE, comment=NA}
confirmed_cases['Hebei'] # To select the element with a specific name 
```

## c) Total number of confirmed cases reported in China.

```{r, warning=FALSE, message=FALSE, comment=NA}
sum(confirmed_cases) # To get the total
```

## d) Number of cases reported in the capital of China.

```{r, warning=FALSE, message=FALSE, comment=NA}
confirmed_cases['Beijing'] # To select the element with a specific name 
```

## e) Number of cases reported in Inner Mongolia.

```{r, warning=FALSE, message=FALSE, comment=NA}
confirmed_cases['Inner Mongolia'] # To select the element with a specific name 
```












